Determinism, Complexity, and Predictability in Computer Performance

### 2014-04-27 concl.tex
beating this thing into PRE shape...

All of the experiments described in this paper involve a particular
physical system.  We chose that system because its behavior spans a
broad spectrum of classical time series patterns.  Since these
patterns (dynamical chaos, periodicities, noise, etc.) are generic, we
believe that our results will generalize beyond this particular
system.  Testing that claim with different examples is another
important next step---and one that will be critical to validating our
claims about the utility of the dashed line as a heuristic for
determining whether a particular forecast method is well-matched to a
particular task.  Of particular interest would be the class of
so-called \emph{hybrid systems}, which exhibit discrete transitions
between different continuous regimes---e.g., a lathe that has an
intermittent instability or traffic at an internet router, whose
characteristic normal traffic patterns shift radically during an
attack.  Effective modeling and prediction of these kinds of systems
is quite difficult; doing so adaptively and automatically---in the
manner that is alluded to at the end of the previous paragraph---would
be an even more important challenge.

>>>>

All of the experiments described in this paper involve a particular
physical system.  We chose that system because its behavior spans a
broad spectrum of classical time series patterns.  Since these
patterns (dynamical chaos, periodicities, noise, etc.) are generic, we
believe that our results will generalize beyond this particular
system.  Testing that claim with different examples is another
important next step---and one that will be critical to validating our
claims about the utility of the dashed line as a heuristic for
determining whether a particular forecast method is well-matched to a
particular task.  Of particular interest would be the class of
so-called \emph{hybrid systems}~\cite{hybrid}, which exhibit discrete transitions
between different continuous regimes---e.g., a lathe that has an
intermittent instability or traffic at an internet router, whose
characteristic normal traffic patterns shift radically during an
attack.  Effective modeling and prediction of these kinds of systems
is quite difficult; doing so adaptively and automatically---in the
manner that is alluded to at the end of the previous paragraph---would
be an even more important challenge.

### 2014-04-27 pecomplexity.tex
cleaning up post submission
beating this thing into PRE shape...

\documentclass[%
pre,
reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%showpacs,preprintnumbers,
nofootinbib,
nobibnotes,
%bibnotes,
 amsmath,amssymb,
% aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}
%\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{amssymb}
%\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}
\usepackage{xspace}
\usepackage{pifont} % check and x marks
\usepackage{color}
\usepackage{listings}
\lstset{language=C}

@@

\end{abstract}
\pacs{
05.45.Tp    % Time series analysis (nonlinear dynamics)
89.70.-a    % Information theory
89.70.Hj    %   communication complexity
89.70.Cf    %   entropy
05.45.-a    % Nonlinear dynamics
89.75.Kd    %   Patterns (complex systems)
95.75.Wx    % Time series analysis, time variability
95.75.Pq    % Mathematical procedures and computer techniques
07.05.-t    % Computers in experimental physics
}

@@

\section*{Acknowledgment}
This work was partially supported by NSF grant \#CMMI-1245947 and ARO
grant \#W911NF-12-1-0288.

\bibliographystyle{aipauth4-1}
\bibliography{bibliofile}

>>>>

\documentclass[%
pre,
reprint,
superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
showpacs,
%preprintnumbers,
nofootinbib,
nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-1}
%\documentclass{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
%\geometry{letterpaper}                   % ... or a4paper or a5paper or ...
%\geometry{landscape}                % Activate for for rotated page geometry
%\usepackage[parfill]{parIEEEabrvskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage[sort&compress]{natbib}
%\usepackage{caption}
\usepackage{subcaption}
\usepackage{microtype}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage{amssymb}
%\usepackage{amsmath}
\usepackage{epstopdf}
\usepackage{amsthm}
\usepackage{xspace}
\usepackage{pifont} % check and x marks
\usepackage{color}
\usepackage{listings}
\lstset{language=C}

@@

\end{abstract}
\pacs{
05.45.Tp    % Time series analysis (nonlinear dynamics)
89.70.-a    % Information theory
%89.70.Hj    %   communication complexity
%89.70.Cf    %   entropy
%05.45.-a    % Nonlinear dynamics
89.75.Kd    %   Patterns (complex systems)
%95.75.Wx    % Time series analysis, time variability
95.75.Pq    % Mathematical procedures and computer techniques
%07.05.-t    % Computers in experimental physics
}

@@

\section*{Acknowledgment}
This work was partially supported by NSF grant \#CMMI-1245947 and ARO
grant \#W911NF-12-1-0288.
We would also like to acknowledge the Santa Fe Institute whose interdisciplinary halls created a place for this work to be born.

%\bibliographystyle{aipauth4-1}
\bibliographystyle{apsrev4-1}
\bibliography{bibliofile}
